### 2018-07-23 express2018/related.tex
Minor typesetting optimizations

\hl{Monica Nesi made the first CCS formalisations for both pure and
value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
theorem prover.\footnote{Part of her old proof scripts is available at
  \url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.}.
Her main focus was on implementing decision procedures (as ML functions) for
automatically proving bisimilarities of CCS
processes. %, thus she stopped proving deeper theorems in Milner's
           %book, once the congruence and algebraic laws of 
%strong, weak and rooted bisimilarity were proved.
\hl{Her work is
  the working basis of ours. However, the differences are substantial, especially in the way of defining
bisimilarities. We greatly benefited from features and standard
libraries in recent versions of HOL4, and our formalisation has
covered a much larger spectrum of the whole theory.}

>>>>

\hl{Monica Nesi made the first CCS formalisations for both pure and
value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
theorem prover.\footnote{Part of her old proof scripts is now available at
  \url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.}.
Her main focus was on implementing decision procedures (as ML functions) for
automatically proving bisimilarities of CCS
processes. %, thus she stopped proving deeper theorems in Milner's
           %book, once the congruence and algebraic laws of 
%strong, weak and rooted bisimilarity were proved.
\hl{Her work is
  the working basis of ours. However, the differences are substantial, especially in the way of defining
bisimilarities. We greatly benefited from features and standard
libraries in recent versions of HOL4, and our formalisation has
covered a much larger spectrum of the whole theory.}
